Create Figures and Tables

### 2023-11-02 Codes/2_figures_tables.rmd
modify readme

saveRDS(hpa_simplified, here("Data/data-processed/hpa_simplified.shp"))
```

```{r}
#--- hpa ---#
hpa_simplified <-
  here("Data/data-processed/hpa_simplified.shp") %>%
  readRDS()

@@

#--- all relevant counties ---#
all_counties <- readRDS("Shared/Data/counties.rds")

#--- all relevant states ---#
all_states <- readRDS("Shared/Data/states.rds")

>>>>

saveRDS(hpa_simplified, here("Data/data-processed/hpa_simplified.rds"))
```

```{r}
#--- hpa ---#
hpa_simplified <-
  here("Data/data-processed/hpa_simplified.rds") %>%
  readRDS()

@@

#--- all relevant counties ---#
all_counties <- readRDS("Data/data-processed/counties.rds")

#--- all relevant states ---#
all_states <- readRDS("Data/data-processed/states.rds")
